A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2014-02-22 jacobian_calc_CMAME.tex
working on peridynamics section, considering citing appendix from seleson paper and reproducing that verbatim in the appendix of this work

\begin{figure}[tbp] \centering \includegraphics[width=0.7\textwidth, height=30px]{./figs/truss.png}
\caption{Beam and spring simulated in example program.} \label{fig:TrussSchematic}
\end{figure}

@@

The type of material model used in this study is referred to as a linear
peridynamic solid, having what is called a state-based constitutive model. In
order for a definition of this material to be useful here, background material
needs to be laid out to enable the discussion. To begin with, some essential
mathematical definitions will be listed and peridynamic theory summarized. Then
state-based constitutive models will be summarized, followed by a description of
the linear peridynamic solid model used in this work. After the peridynamic
equation of motion and consitutive model in use have been discussed, it is then
possible to give a more precise definition of the tangent stiffness matrix for
the problem being discussed in this work. The following discussion is largely
taken from \cite{silling:psa}, but reproduced here fo clarity.

@@

\subsubsection{State-based consitutive models.}

@@

\note[Michael]{re: I.2} \add[Michael]{
\subsubsection{The tangent stiffness matrix in a quasi-static peridynamic simualtion.}
The tangent stiffness matrix is the frechet derivative of the residual wrt the
deformation state.  For the purposes of this work, the residual represents the unbalanced forces in the
equilibrium version of the peridynamic equation of motion. The internal force
density is computed in the peridynamic equation of motion by computing the
volume integral over, a horizon, of the Frechet derivative of the 
strain energy state wrt to the deformed configuration inner product with the deformation state, per node,
for each of the three directions in the original reference frame.

For the finite-difference type methods in \emph{Peridigm}, the perturbation
method is employed by probing the deformed configuration one degree of freedom
at a time and so allowing the sensitivity of the force density state wrt the
deformation state for all nodes to be computed.  }

>>>>

\begin{figure}[tbp] \centering \includegraphics[width=0.7\textwidth]{./figs/truss.png}
\caption{Beam and spring simulated in example program.} \label{fig:TrussSchematic}
\end{figure}

@@

The type of material model used in this study is referred to as a linear
peridynamic solid, having what is called a state-based constitutive model. In
order for a definition of this material to be useful her. To begin with, some essential
mathematical definitions will be listed and peridynamic theory summarized. Then
state-based constitutive models will be summarized, followed by a description of
the linear peridynamic solid model used in this work. After the peridynamic
equation of motion and consitutive model in use have been discussed, it is then
possible to give a more precise definition of the tangent stiffness matrix for
the problem being discussed in this work. The following discussion is largely
taken from \cite{silling:psa} but reproduced here for clarity.

@@

In \cite{silling:psa}, the primary reference for state based peridynamics, the
equation of motion for state based peridynamic theory is derived. No
development of the theory is claimed; the equation of motion is reproduced here for the reader's convenience.
%
The general equation is written as it appears in \cite{silling:psa}:
\begin{equation} 
    \label{eqn:PDMotion}
    \rho(\boldsymbol{x})\boldsymbol{\ddot{u}}(\boldsymbol{x}, t) = \int_{\mathcal{H}_{\boldsymbol{x}}} \{\boldsymbol{\underline{T}}[\boldsymbol{x}, t]\langle \boldsymbol{x}^{\prime} - \boldsymbol{x} \rangle - \boldsymbol{\underline{T}}[\boldsymbol{x}^{\prime}, t]\langle \boldsymbol{x} - \boldsymbol{x}^{\prime} \rangle \}dV_{\boldsymbol{x}^{\prime}} + \boldsymbol{b}(\boldsymbol{x}, t),
\end{equation}

where "$\mathcal{H}_{\boldsymbol{x}}$ is a spherical neighborhood" with a
radius, centered at the original coordinates of a peridynamic node,
$\boldsymbol{x}$, and \boldsymbol{\underline{T}} is the "force vector state
field". The force vector state field maps vectors in the original coordinate system 
measured from the peridynamic node at the center of the neighborhood or 'horizon' to
neighboring peridynamic nodes that fall within the radius of the horizon. $\boldsymbol{b}$ denotes a body force density. Equation~\ref{eqn:PDMotion} may be simplified based on the assumption that
\boldsymbol{\underline{T}} is Riemann integrable and that integral is uniformly
convergent \cite{silling:psa} as,

\begin{equation} 
    \label{eqn:PDMotion_simple}
    \rho\boldsymbol{\ddot{u}} = \int_{\mathcal{H}_{\boldsymbol{x}}} \{\boldsymbol{\underline{T}}\langle \boldsymbol{x}^{\prime} - \boldsymbol{x} \rangle - \boldsymbol{\underline{T}}^{\prime}\langle \boldsymbol{x} - \boldsymbol{x}^{\prime} \rangle \}dV_{\boldsymbol{x}^{\prime}} + \boldsymbol{b},
\end{equation}

where,

\begin{equation} 
    \label{eqn:PDMotion_simple}
    \boldsymbol{\underline{T}} = \boldsymbol{\underline{T}}[\boldsymbol{x}, t], 
    \boldsymbol{\underline{T}}^{\prime} = \boldsymbol{\underline{T}}[\boldsymbol{x}^{\prime}, t]. 
\end{equation}

@@

\note[Michael]{re: I.2} \add[Michael]{
\subsubsection{The tangent stiffness matrix in a quasi-static peridynamic simualtion.}
The tangent stiffness matrix is the Frechet derivative of the residual wrt the
deformation state.  For the purposes of this work, the residual represents the unbalanced forces in the
static peridynamic momentum equation. The internal force
density is computed in the peridynamic momentum equation by computing the
volume integral over a horizon of the Frechet derivative of the 
strain energy density state wrt to the deformed configuration inner product with the deformation state, per node,
for each of the three directions in the original reference frame.

For the finite-difference type methods in \emph{Peridigm}, the perturbation
method is employed by probing the deformed configuration one degree of freedom
at a time and so allowing the derivative of the force density state wrt the
deformation state for all nodes to be computed. 
}
